DOpElib: Differential Equations\\ and Optimization Environment

### 2013-05-08 Examples/Documentation/introduction.tex
Updated the documentation

\subsection{Reduced problems (Solve the PDE)}
At times it is nice to remove the PDE constraint in (OPT). 
This is handled by so called reduced 
problems (for algorithmic aspects we refer the reader to 
\cite{BeMeVe06}). 
This means that the reduced problem implicitly solves the PDE whenever required
and eliminates the variable $u$ from the problem.
\begin{itemize}
\item \texttt{reducedproblems/statpdeproblem.h} This is used to remove the variable $u$ in 
  a stationary PDE problem. This means that call the method \\
  \texttt{StatPDEProblem::ComputeReducedFunctionals} will evaluate the functionals 
  defined in the problem description, i.e., in \texttt{PDEProblemContainer}, in the 
  solution of the given PDE.
\item \texttt{reducedproblems/statreducedproblem.h} This eliminates $u$ from the OPT
  problem with a stationary PDE.
\item \texttt{reducedproblems/instatreducedproblem.h} The same as above but for a
  nonstationary PDE.
\item \texttt{reducedproblems/voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint.
\end{itemize}

\subsection{Optimization algorithms}
Now, in order to solve optimization algorithms we need to define some algorithms.
At present we offer a selection of algorithms that solve the reduced optimization 
problem where the PDE constraint has been eliminated as explained in the previous section.
\begin{itemize}
\item \texttt{opt\underline{ }algorithms/reducedalgorithm.h} An interface for all 
  optimization problems in the reduced formulation. It offers some test functionality
  to assert that the derivatives of the problem are computed correctly.
\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithm.h}
  A line-search Newton algorithm using a cg method to invert the reduced hessian. 
  Implementation ignores any additional constraints.
\item \texttt{opt\underline{ }algorithms/reducedtrustregionnewton.h}
  A trust region Newton algorithm using a cg method to invert the reduced hessian.
  Implementation ignores any additional constraints.
\item \texttt{opt\underline{ }algorithms/reduced\underline{ }snopt\underline{ }algorithm.h}
  An algorithm to solve reduced optimization problems with additional control constraints.
  ((reduced) state constraints are not yet implemented.)
\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithmwithinverse.h}
  Line-search Newton algorithm that assumes there exists a method in the reduced problem
  that can invert the reduced hessian. (This usually makes sense only if there is no 
  PDE constraint.)
\item \texttt{opt\underline{ }algorithms/generalized\underline{ }mma\underline{ }algorithm.h}
  An implementation of the MMA-Algorithm for structural optimization using an augmented
  Lagrangian formulation for the subproblems. The subproblem is implemented using the 
  special purpose file
  \texttt{include/augmentedlagrangianproblem.h}.
\end{itemize}

>>>>

\subsection{Reduced problems (Solve the PDE)}
At times it is nice to remove the PDE constraint in (OPT). 
This is handled by so called reduced 
problems (for algorithmic aspects we refer the reader to 
\cite{BeMeVe06}). 
This means that the reduced problem implicitly solves the PDE whenever required
and eliminates the variable $u$ from the problem.
\begin{itemize}
\item \texttt{reducedproblems/statpdeproblem.h} This is used to remove the variable $u$ in 
  a stationary PDE problem. This means that call the method \\
  \texttt{StatPDEProblem::ComputeReducedFunctionals} will evaluate the functionals 
  defined in the problem description, i.e., in \texttt{PDEProblemContainer}, in the 
  solution of the given PDE.
\item \texttt{reducedproblems/statreducedproblem.h} This eliminates $u$ from the OPT
  problem with a stationary PDE.
\item \texttt{reducedproblems/instatreducedproblem.h} The same as above but for a
  nonstationary PDE.
\item \texttt{reducedproblems/voidreducedproblem.h} A wrapper file that eliminates $u$ 
  if it is not present anyways. This is used so that we can use the same routines to 
  solve problems that have no PDE constraint.
\item \texttt{reducedproblems/ipopt\underline{ }problem.h} A wrapper file that is used by the 
  reduced\underline{ }ipopt\underline{ }algorithm when solving optimization problems. This file
  hides the interface to IPOPT.
\end{itemize}

\subsection{Optimization algorithms}
Now, in order to solve optimization algorithms we need to define some algorithms.
At present we offer a selection of algorithms that solve the reduced optimization 
problem where the PDE constraint has been eliminated as explained in the previous section.
\begin{itemize}
\item \texttt{opt\underline{ }algorithms/reducedalgorithm.h} An interface for all 
  optimization problems in the reduced formulation. It offers some test functionality
  to assert that the derivatives of the problem are computed correctly.
\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithm.h}
  A line-search Newton algorithm using a cg method to invert the reduced hessian. 
  Implementation ignores any additional constraints.
\item \texttt{opt\underline{ }algorithms/reducedtrustregionnewton.h}
  A trust region Newton algorithm using a cg method to invert the reduced hessian.
  Implementation ignores any additional constraints.
\item \texttt{opt\underline{ }algorithms/reduced\underline{ }snopt\underline{ }algorithm.h}
  An algorithm to solve reduced optimization problems with additional control constraints
  using the third-party library SNOPT.
  ((reduced) state constraints are not yet implemented.)
\item \texttt{opt\underline{ }algorithms/reduced\underline{ }ipopt\underline{ }algorithm.h}
  An algorithm to solve reduced optimization problems with additional control constraints.
  using the third-party library IPOPT.
  ((reduced) state constraints are not yet implemented.)
\item \texttt{opt\underline{ }algorithms/reducednewtonalgorithmwithinverse.h}
  Line-search Newton algorithm that assumes there exists a method in the reduced problem
  that can invert the reduced hessian. (This usually makes sense only if there is no 
  PDE constraint.)
\item \texttt{opt\underline{ }algorithms/generalized\underline{ }mma\underline{ }algorithm.h}
  An implementation of the MMA-Algorithm for structural optimization using an augmented
  Lagrangian formulation for the subproblems. The subproblem is implemented using the 
  special purpose file
  \texttt{include/augmentedlagrangianproblem.h}.
\end{itemize}
